Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-23 cav2017/cav2017.tex
text

Program synthesizers are an ideal fit for synthesis of %parametric
controllers since the semantics of programs capture effects such as FWL
precisely.  In~\cite{DBLP:conf/cdc/RavanbakhshS15}, the authors use CEGIS
for the synthesis of switching controllers for stabilising continuous-time
plants with polynomial dynamics.  The work extends to its application on
affine systems, finding its major challenge in the hardness of solving
linear arithmetic with the state-of-the-art SMT solvers.  Since this
approach uses switching states instead of linear dynamics in the digital
controller, it entirely circumvents the FWL problem.  It is also not
suitable for the kind of control we seek to synthesise.

%\textcolor{red}{Cristina: can you please revise this sentence:
Moreover, in \cite{DBLP:conf/emsoft/RavanbakhshS16} the same authors 
use a CEGIS-based approach for synthesising continuous-time switching
controllers that guarantee Reach While Stay properties of closed
loop systems, i.e., properties that specify a set of goal states and safe states.%}. 
The solution is based on synthesising control Lyapunov
functions for switched systems, that yield switching controllers with
a guaranteed minimum dwell time in each mode.

@@

The tool Pessoa~\cite{mazo2010pessoa} is a MatLab toolbox that synthesises correct-by-design
embedded control software. It is based on the principle of describing a physical system
as an equivalent finite-state machine and computing reachability over the finite-state 
machine. Pessoa can synthesise safe embedded controller software for a range of properties based on a safety specification over state
values, as well as specification on characteristic functions of the controller. 
However, Pessoa does not have native inclusion of the ADC/DAC quantization error needed for
synthesising a fixed-point digital controller.

We use a combination of a synthesis engine with a control
verification tool that addresses the challenges presented here in the
form of FWL effects and stability measures for LTI SISO controllers.

We take the former from~\cite{DBLP:conf/lpar/DavidKL15}. The verification engine, for
the first approach we present, performs bounded model checking of control properties,
based on~\cite{Monteiro16}, but 
enhanced to include evaluation of quantization effects and safety properties
over the state space. In the second approach, we use a verification engine
based on abstract acceleration~\cite{cattaruzza2015unbounded} than avoids the explicit 
unwinding the transition system necessarily for the first approach.

>>>>

Program synthesizers are an ideal fit for synthesis of %parametric
digital controllers, since the semantics of programs capture effects such as FWL
precisely.  In~\cite{DBLP:conf/cdc/RavanbakhshS15}, the authors use CEGIS
for the synthesis of switching controllers for stabilising continuous-time
plants with polynomial dynamics.  The work extends to affine systems, 
finding a major challenge in the hardness of solving linear arithmetic with the state-of-the-art SMT solvers.  
Since this approach uses switching models instead of linear dynamics for the digital controller, 
it entirely circumvents the FWL problem, but potentially incurs state-space explosion issues.  
This approach is not suitable for the kind of control we seek to synthesise.

%\textcolor{red}{Cristina: can you please revise this sentence:
Moreover, in \cite{DBLP:conf/emsoft/RavanbakhshS16} the same authors 
use a CEGIS-based approach for synthesising continuous-time switching
controllers that guarantee \emph{reach-while-stay} properties of closed-loop systems, 
i.e., properties that specify a set of goal states and safe states (constrained reachability).%}. 
The solution is based on synthesising control Lyapunov 
functions for switched systems, that yield switching controllers with
a guaranteed minimum dwell time in each mode.

@@

The tool Pessoa~\cite{mazo2010pessoa} is a MatLab toolbox that synthesises correct-by-design
embedded control software. It is based on the description of a physical system
as an equivalent finite-state machine and on the computation of reachability properties over the finite-state 
machine. 
Based on this safety specification over state values, 
Pessoa can synthesise embedded controller software for a range of properties.  
%based on a safety specification over state values, as well as specification on characteristic functions of the controller. 
However, Pessoa does not have native inclusion of the ADC/DAC quantisation error needed for
synthesising fixed-point digital controllers.

We use a combination of a synthesis engine with a control
verification tool that addresses the challenges presented in the
form of FWL effects and stability measures over digital controllers for LTI models.

We take the synthesis engine from~\cite{DBLP:conf/lpar/DavidKL15}. The verification engine, for
the first approach we present, performs bounded model checking of control properties,
based on~\cite{Monteiro16}, but enhanced to include evaluation of quantisation effects and safety properties
over the state space. In an alternative approach, we use a verification engine based on abstract acceleration~\cite{cattaruzza2015unbounded}, 
which avoids the explicit unwinding the transition system necessarily for the first approach.
